Manuscript

### 2019-01-25 manuscript.Rmd

floatsintext      : yes
figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

(ref:crispr-waterfall) Stuff stuff stuff!

>>>>

floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

(ref:crispr-waterfall) **CRISPR screen correlations between  dependencey score, gene expression, and copy number**. Significance of Spearman correlation coefficients ($r_s$) derived from comparisons of CERES score/gene expression and CERES score/copy number for the `r length(crispr_signif_g2p_gene$Hugo_Symbol)` G2P genes screened in the CRISPR dataset. Inset plots show example derivations of Spearman correlation coefficients using *KRAS* gene expression (left) and copy number (right). In both inset plots, each point represents data from one cell line.
